Multi-Agent Path Finding with Matching using Increasing Cost Tree Search

### 2021-06-14 docs/paper.tex
Updated plots in paper

	\begin{figure*}
	\centering
	\begin{subfigure}{0.40\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/counter-example-ep-2}
		\caption{Instance}
		\label{fig:counter-example:a}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/counter-example-tree}
		\caption{Pruned ICT that is traversed}
		\label{fig:counter-example:b}
	\end{subfigure}
		\caption{Counter-example for E+C pruning}
		\label{fig:counter-example}
	\end{figure*}
	\begin{figure*}
		\centering
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/open-1}
			\caption{Open, 1 team}
			\label{fig:open1}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/open-3}
			\caption{Open, 3 teams}
			\label{fig:open3}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/obstacle-1}
			\caption{Obstacle, 1 team}
			\label{fig:obstacle1}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/obstacle-3}
			\caption{Obstacle, 3 teams}
			\label{fig:obstacle3}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-1}
			\caption{Maze, 1 team}
			\label{fig:m1}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-3}
			\caption{Maze, 3 teams}
			\label{fig:m3}
		\end{subfigure}
		\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
		\label{fig:times}
	\end{figure*}

	\begin{figure*}
		\centering
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/open-1-p}
			\caption{Open, 1 team}
			\label{fig:open1p}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/open-3-p}
			\caption{Open, 3 teams}
			\label{fig:open3p}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/obstacle-1-p}
			\caption{Obstacle, 1 team}
			\label{fig:obstacle1p}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/obstacle-3-p}
			\caption{Obstacle, 3 teams}
			\label{fig:obstacle3p}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-1-p}
			\caption{Maze, 1 team}
			\label{fig:maze1p}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-3-p}
			\caption{Maze, 3 teams}
			\label{fig:maze3p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps of algorithm variants on various types of 20x20 grids with a 30s timeout}
		\label{fig:probs}
	\end{figure*}

>>>>

	\begin{figure*}
	\centering
	\begin{subfigure}{0.40\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/counter-example-ep-2}
		\caption{Instance}
		\label{fig:counter-example:a}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/counter-example-tree}
		\caption{Pruned ICT that is traversed}
		\label{fig:counter-example:b}
	\end{subfigure}
		\caption{Counter-example for E+C pruning}
		\label{fig:counter-example}
	\end{figure*}
	\begin{figure*}
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
		\caption{25, 1 team}
		\label{fig:open1p}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
		\caption{25, 3 teams}
		\label{fig:open3p}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
		\caption{75, 1 team}
		\label{fig:obstacle1p}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
		\caption{75, 3 teams}
		\label{fig:obstacle3p}
	\end{subfigure}
	\caption{Fraction solved out of 50 maps of algorithm variants on two types of 20x20 grids with a 120s timeout}
	\label{fig:probs}
	\end{figure*}
	\begin{figure*}
		\centering
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
			\caption{25, 1 team}
			\label{fig:25-1}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
			\caption{25, 3 teams}
			\label{fig:25-3}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
			\caption{75, 1 team}
			\label{fig:75-1}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
			\caption{75, 3 teams}
			\label{fig:75-3}
		\end{subfigure}
		\caption{Average solving time of algorithm variants on two types of 20x20 grids with a 120s timeout}
		\label{fig:times}
	\end{figure*}
